Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-04 paper-2024-sac-marl-neighbouring-strategies.tex
add link to anonymous gh

\usepackage{booktabs} % For formal tables
\usepackage{graphicx}
\usepackage{autobreak}
\usepackage{mytodonotes}
\usepackage{subcaption}
\usepackage[inline]{enumitem}
\usepackage[ruled,vlined]{algorithm2e}
%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{cleveref}

@@

@@

% Reward 
\subsection{Reward}
One of the most important aspects in MARL is how the reward signal that the agents use to 
  learn is defined.
%
In particular, we have defined a reward function composed of many subcomponents.

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{graphicx}
\usepackage{autobreak}
\usepackage{mytodonotes}
\usepackage{subcaption}
\usepackage{url}
\usepackage[inline]{enumitem}
\usepackage[ruled,vlined]{algorithm2e}
%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{cleveref}

@@

We ran a total of $35$ training experiments, namely: $5$ different methods 
  (centralized, distributed and neighbor based approaches), and for each method we ran multiple experiments
  varying the random seed (7 seeds) to obtain stronger results. 
%
Each experiment consisted of $50$ training episodes.

Furthermore, we ran $15$ evaluation experiments, namely: $5$ different methods and for each method 
  we varied the number of agents ($8$, $16$ and $32$) to assess the metrics under various conditions.
  In this case, for each experiment we ran $100$ evaluation episodes.

All the experiments are publicly available and reproducible\footnote{\url{https://anonymous.4open.science/r/experiments-2024-SAC-marl-neighbouring-strategies-4B8F}}.

@@

\subsection{Reward}
One of the most important aspects in MARL is how the reward signal that the agents use to 
  learn is defined.
%
In particular, we have defined a reward function composed of many subcomponents.
